%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.2 (3/28/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Modified by:
% Daniel L Marks <xleafr@gmail.com> 3/28/2015
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% You can have multiple style options the legal options ones are:
%
%   centered:	the name and address are centered at the top of the page 
%				(default)
%
%   line:		the name is the left with a horizontal line then the address to
%				the right
%
%   overlapped:	the section titles overlap the body text (default)
%
%   margin:		the section titles are to the left of the body text
%		
%   11pt:		use 11 point fonts instead of 10 point fonts
%
%   12pt:		use 12 point fonts instead of 10 point fonts
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[margin]{res}  

% Default font is the helvetica postscript font
\usepackage{helvet}
\usepackage{hyperref}

% Increase text height
\textheight=700pt

\begin{document}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
\name{James Woods}

% Note that addresses can be used for other contact information:
% -phone numbers
% -email addresses
% -linked-in profile

\address{10612 NE Sacramento\\Portland, OR 97220\\503.465.4883}
\address{pdxwoodsj@gmail.com\\ \href{https://github.com/woodsjam/James-Woods-CV/blob/master/vita_current.pdf}{Full CV Available}}

% Uncomment to add a third address
%\address{Address 3 line 1\\Address 3 line 2\\Address 3 line 3}
%-------------------------------------------------------------------------------

\begin{resume}

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{Education}
\textbf{University of California, Davis}, Davis, CA\\
{\sl Ph.D.}, Economics, 2003

\textbf{University of The Pacific}, Stockton, CA\\
{\sl B.Sc.}, Economics, 1991

%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	PROJECTS SECTION
%-------------------------------------------------------------------------------
\section{Selected Employment and Governance Boards}

% Modify the format of each position
\begin{format}
\title{l}\employer{r}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------

\employer{\textbf{Portland State University}}
\location{Portland, OR}
\dates{2014 - Current}
\title{\textbf{Assistant Professor}}
\begin{position}
Courses Taught: Engineering Economics, Energy Economics, Public Utility Economics, Project Evaluation, Behavioral Economics, Graduate Microeconomic Theory

Supervision of multiple theses, term papers, most often in energy economics and program evaluation. Major grants from the California Energy Commission on residental consumer behavior. 

\end{position}

\employer{\textbf{Behavioral Economics}}
\location{Portland, OR}
\dates{2001 - Current}
\title{\textbf{Owner}}
\begin{position}
Small consultancy focusing on energy efficiency evaluation.

Projects include evaluation of:
\begin{itemize}
\item Time-of-Use tariffs for Sacramento Municipal Utility District (SMUD) with report to Lawrence Berkeley National Laboratory (LBNL)
\item Kilowatt Crackdown with presentation  and delivery to Northwest Energy Efficiency Alliance (NEEA).
\end{itemize}

\end{position}

\employer{\textbf{External Review Board, Energy Trust of Oregon}}
\location{Portland, OR}
\dates{2017 - Current}
\title{\textbf{Member}}
\begin{position}
This is an appointed possition that provides external review of evaluations to ensure quality and validity of program evaluations.


\end{position}


\employer{\textbf{Higher Education Coordinating Commission}}
\location{Salem, OR}
\dates{2012 - 2013}
\title{\textbf{Commissioner}}
\begin{position}
I was appointed to this rule making body by Governor Kitzhaber.

Major acomplishments include:
\begin{itemize}
\item Passage of OARs related to the Office of Degree Authorization
\item Funding formulas for Oregon's public universities and community colleges and;
\item A report on textbook cost.
\end{itemize}

\end{position}

\employer{\textbf{Parkrose Board of Education}}
\location{Portland, OR}
\dates{2005 - 2013}
\title{\textbf{Director}}
\begin{position}
This is an elected possition.  I spent six years as either chair or vice-chair.

Supervision of budget process, policy development, handling of constituent concerns,townhalls, lobbying state, county and city elected officials.

Major Acomplishments: 

\begin{itemize}
\item Passage of construction bond, 
\item Sucessful construction of a new middle school, 
\item A variety of policies that were later adopted statewide.
\item Establishing the ACE Academy for Architecture, Construction and Engineering
\end{itemize}

\end{position}

%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
% \section{COMPUTER\\SKILLS}
% 
% \textbf{Languages}: C, C++, Java, ML, Perl, Bash, Assembly, SQL, \LaTeX.
% \\
% \textbf{Web Development}: HTML, CSS, JavaScript, PHP, Apache, IIS, ASP.NET.
% \\
% \textbf{Applications}: Vi/Vim, Eclipse, Visual Studio, Git, VMWare, VirtualBox, 
% MySQL, Oracle 11g.
% \\
% \textbf{Operating Systems}: 
% Unix, Linux, FreeBSD, Mac OSX, Windows, Android.
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%-------------------------------------------------------------------------------
\section{Selected Projects}
\par
\textbf{HB 4058 Report To Legislature on Textbook Affordability}: 

Chaired a report to the legislature on a short, 3-month timeline.  Recruited workgroup. Negotiated with OUS for staffing, held multiple public hearings, and produced recomendations.

The legislature did not provide a budget for this report and had not allocated funds to the Higher Education Coordinating Commision at that time.  The primary difficulty was recruiting a volunteer panel and staff and producing recomendations in three months when efforts in other states were given a year or more.

\par

\textbf{Economics of Improved Indoor Air Quality and the Use of Construction Methods that Promote Building Durability in Affordable Multi-Family Dwellings}:

This was three projects in one and combined:
\begin{itemize}
\item A cost effectivness evaluation with priors on installation and damage rates 
\item A Bayesian method to estimate the costs of indoor airpolution.
\item Several Multi-hour interviews of maintance supervisors.
\end{itemize}

I took this project with the Portland  Development Commission over after the project started. I developed a work plan; hired students with needed expertise in organic chemistry, content analysis, ethnographic interviews and Bayesian statistics and; and managed the project to completion.




%-------------------------------------------------------------------------------
%	Interests
%-------------------------------------------------------------------------------
% \section{INTERESTS}
% Interest One, Interest Two, Interest Three, Interest Four, ...Et Cetera.
%-------------------------------------------------------------------------------
\end{resume}
\end{document}